### 2020-09-25 mathematics.tex
debug AT-diagonalize code

Sample Mathematica code to calculate $\{D,R\}$ (with ordering, if specified) is:
\begin{minted}{wolfram}
AutonneTakagi[M_, order_ : None] := Module[{v, p, ord, R, D},
  ord = If[order === None, Range[Length[M]], order];
  v = Transpose[SingularValueDecomposition[M][[3]]];
  p = DiagonalMatrix[(#/Abs[#])^(-1/2) & /@ Diagonal[v.M.Transpose[v]]];
  R = ConjugateTranspose[Reverse[p.v][[ord]]];
  D = ConjugateTranspose[R].M.Conjugate[R];
  {D, R} ];
\end{minted}
\end{document}

>>>>

Sample Mathematica code to calculate $\{D,R\}$ (with ordering, if specified) is:
\begin{minted}{wolfram}
AutonneTakagi[M_, order_ : None] := Module[{v0, v, p, ord, R, D},
  ord = If[order === None, Range[Length[M]], order];
  v0 = Eigenvectors[Conjugate[M].M];
  v = Eigenvectors[v0.M.Transpose[v0]].v0; (*resolve degenerate eigenvalues*)
  p = DiagonalMatrix[If[Abs[#] > 0, (#/Abs[#])^(-1/2), 1] & /@ Diagonal[v.M.Transpose[v]]];
  R = ConjugateTranspose[Reverse[p.v][[ord]] // Orthogonalize];
  D = ConjugateTranspose[R].M.Conjugate[R];
  {D, R}];
\end{minted}
\end{document}
